---
title: "Blog Post 4"
author: "Bryan Bittner"
date: '2022-07-16'
output: 
  github_document: default
   
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,fig.path = "../images/")

library(tidyverse)
library(class)
```

```{r, eval=FALSE}
rmarkdown::render("_Rmd/2022-07-16-blog-post-MachineLearning.Rmd", 
                  output_format = "github_document",
                  output_dir = "./_posts",
                  output_options = list(
                    html_preview= FALSE
                    )
)
```

## Blog Post 5 - Machine Learning

We have learned a lot of different modeling types and machine learning methods. All of which are very interesting and have their specific uses. I would have to say that I think the coolest model that we learned about would have to be the kNN nearest neighbor. 

kNN is a supervised machine learning method meaning it relies on manually inputted data in order to learn and produce accurate output. kNN can be used on both classification problems as well as regression problems.

The basics for kNN is that you use the "closest" k number of observations to determine the prediction with the highest probability. The kNN algorithm assumes that similar things are near each other. The kNN algorithm will calculate the distance between points and determine the likely outcome.

For an example, we can look at the traditional 'iris' dataset.

```{r}
data(iris)
head(iris)
```

Before we do any modeling, lets split up the dataset into a training set and a test set.

```{r}
train <- sample(1:nrow(iris),size=nrow(iris)*.8)
test <- dplyr::setdiff(1:nrow(iris),train)

irisDataTrain <- iris[train,]
irisDataTest <- iris[test,]
head(irisDataTrain)
```

In order to fit a kNN model, we need to load the class library. 
For the model fit, we will pass in the training data and use the test data to determine how accurate the model predictions are. Here we will use the sepal.length and sepal.width as our predictors and the Species as the response variable.

```{r}
knnFit <- knn(train = select(irisDataTrain, Sepal.Length, Sepal.Width),
              test = select(irisDataTest, Sepal.Length, Sepal.Width),
              cl = irisDataTrain$Species,
              k = 3)
fitInfo <- as_tibble(data.frame(knnFit, select(irisDataTest, Species, Sepal.Length, Sepal.Width)))
fitInfo
```
Now that the model has been fit, we can use this table below to see how accurate the predictions were. There are three different types of species. The numbers on the diagonal column from left to right are the predictions that were correct. All of the other values in the table are predictions that were incorrect. As you can see, overall it looks like the kNN model did a great job at predicting.

```{r}
tbl1 <- table(fitInfo$knnFit,fitInfo$Species)
tbl1
```
Here we can get an actual value to see how accurate the model is. The value below is a 'mis-classification rate'. Meaning this is how often the kNN model predicted the incorrect Species type.

```{r}
misClass <- 1 - sum(diag(tbl1))/sum(tbl1)
misClass
```
Overall the kNN model did a pretty good job at predicting. One way to improve the mis-class rate would be to utilize cross validation.
