---
title: "Project 1"
author: "Bryan Bittner"
date: '2022-06-24'
output: 
  github_document: default
   
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,fig.path = "../images/")
```

```{r, eval=FALSE}
rmarkdown::render("_Rmd/2022-06-24-blog-post-Project1.Rmd", 
                  output_format = "github_document",
                  output_dir = "./_posts",
                  output_options = list(
                    html_preview= FALSE
                    )
)
```

## Project 1 Blog Post

In my current position, one of my job duties is to forecast revenue for the state of North Dakota. With the list of api's to choose from, I naturally gravitated to the Financial Data api.In the beginning, I did not have a plan for the data. As soon as I started querying the data and running my EDA, a storyline quickly developed.

In order to forecast revenue, I need to be aware of how things outside of the state might influence revenue the state receives. Typically this would center around oil and agricultural prices, but I also need to be aware of changes at the federal level. On June 14th the Federal Reserve raised interest rates by 0.75 percentage points. This will in turn raise rates on everyone or any company that needs a loan. This of could will require all individuals and businesses to spend more money. When a business has to spend more money, their stock typically will go down as well. Going into this project, I was aware that the stocks took a bit of a hit when the rate change was made. I was not aware of the anticipation and trendline that accompanies the said decision.

Overall I think this was a very neat project and I'm glad I had the chance to work on it. One of the most difficult things I had was the fact that the free version of this API had a count limit. This limit wasn't an issue when I was manually running the code chunks, but it caused me some time when I went to render the code. In the end I found the problem and just payed to get those counts increased. A small price to pay to have an efficient and well laid out project!

If I had to do a similar project again, I probably would have spent a bit more time in the analysis phase instead of jumping into the code. In the end it probably could have saved some time if I laid out a plan before writing code. Overall though I think things went pretty smooth.

[Here is a link to my github pages repo:](https://bbittne.github.io/)

[Here is a link to my regular repo:](https://github.com/bbittne/Project1)


