---
title: "Project 1"
author: "Bryan Bittner"
date: '2022-07-08'
output: 
  github_document: default
   
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,fig.path = "../images/")
```

```{r, eval=FALSE}
rmarkdown::render("_Rmd/2022-07-08-blog-post-Project2.Rmd", 
                  output_format = "github_document",
                  output_dir = "./_posts",
                  output_options = list(
                    html_preview= FALSE
                    )
)
```

## Project 2 Blog Post

This project is centered around a real life news data set. The end goal of the project is to try to analyze and model the data set, as well as try to predict the number of shares. This required knowledge of all aspects that we have been taught so far in this course, as well as a few new things that we had to learn along the way.

One of the most interesting aspects of this project was the 'automation' portion. This required additional code that would allow us to pass in a particalar news channel as a parameter. The report would then automatically subset the news data to that specific channel and run the analysis and modeling on that single channel. As the parameter channels change, the report will change along with it.

If more time was allowed in the project, I would have spent additional time and effort on some of the summarizations and models. I think there are additional insights that could have been drawn out from the vast dataset that were left untouched. We worked on the data as a subset, I think it would have also been interesting to do some modelling using the whole dataset to see if that would have changed any predictions.

The most difficult part for me was the automation portion. There is a lot going on in that small code block so not only is it a lesser known feature, it is not very intiutive. Having said that, it is definitely a cool feature and it works great!!

Overall I think this was a good project. Working with a team always has its advantages and disadavantages. With this project I had some personal family matters doing on which limited my participation. This meant that Li did more than her fair sure of work. I greatly apprecated that but also feel bad about putting her in that position. Parameter driven reports/projects are widely used across industry so it is good to work on a real lifelike example of what we will encounter outside of the classroom.

[Here is a link to the github pages site:](https://bbittne.github.io/ST558-Project2/)

[Here is a link to the project repo:](https://github.com/bbittne/ST558-Project2)


