---
title: "Programming Background"
author: "Bryan Bittner"
date: '2022-06-04'
output: 
  github_document: default
   
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,fig.path = "../images/")
```

## Blog Post 3

Everyone in this course had some programming experience coming in (due to the prerequisites).  What are your thoughts on R vs whatever other software you've used? What functionality do you like about R?  What parts do you miss about your other language?  Do you consider R a difficult language to learn? (If you knew R prior to the course, describe your experience when first learning it.)

Most of my programming experience would revolve around the .net series of languages as well as the SQL database programming language. I have also taken the Python programming course here at NC State. Overall I like R, but if I had to choose between R and Python, I would choose Python. As a software engineer, Python seems more intuitive and easier to work with. I also like the fact that there is a single package to do most things vs R it seems like everyone has their own packages that solve the same problem. 

I haven't hand any other formal training in R besides this course, so the explanations have definitely helped a lot. The use of the tidyverse packages make R easier to work with.

## R Markdown output

```{r}
plot(iris)
```


```{r echo = FALSE}
#rmarkdown::render("_Rmd/2022-06-04-blog-post-Module5.Rmd", 
#	output_format = "github_document", 
#	output_dir = "/_posts"
#	output_options = list(
#		html_document:
#			code_folding: hide,
#		github_document:)
#	)
```

